Word2vec learns effective distance of scientific co-affiliation

### 2020-01-28 paper/current/main.tex
new figure to show how embedding performance differs by choice of params

>>>>

%
% Figure - Hyperparameter performance
%
\begin{figure}[p!]
	\centering
	\label{fig:supp:hyperparams}
	\includegraphics[width=\textwidth]{\figdir/Descriptive/hyperparameter_performance.pdf}
	\caption{
		\textbf{Larger dimensions, smaller window size improves embedding performance.}
		The correlation, or amount of flux explained by the embedding proximity with varying skip-gram negative sampling hyperparameters. 
		Window size refers to the window, on either side of the target token, to use as context for training. 
		Smaller window sizes results in an embedding that explain more of the flux. 
		Embedding dimensions refer to the size of the organization vector.
		Larger vectors perform better, though little difference between 200 and 300. 
		All variants perform better on same-country pairs of organizations than on all organizations.
		All variants perform worse on different-country pairs on organizations.
		Larger embeddings outperform mid-size embeddings for the different-country case.
	}
\end{figure}
